Response to the defense feedback

### 2021-06-18 Chapter-4/Chapter-4.tex
Updates from Overleaf

\begin{figure}[h!]
    \centering
    \begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.0\textwidth, frame=none]
uint8_t password = input();

a = *password & 0b001;
b = (*password & 0b010) >> 1;
c = (*password & 0b100) >> 2;

na = ~a & 1;
nb = ~b & 1;
nc = ~c & 1;

t0 = (b & nc);
t1 = (b | nc);

l = (a & nb) | t0;
r = (na & t1) | t0;

ret = l << 1 + r;
\end{lstlisting}
\caption{SBOX with bitslicing}
\label{fig:SBOX_bitslicing}
\end{figure}
We test \tool\ on bit-slicing. We adopt the SBOX
implementations, commonly used in block ciphers such as DES and AES, with and
without bit-slicing, and apply \tool{} to confirm the mitigation. The SBOX implementation with and without bit-slicing are shown in Figure~\ref{fig:SBOX_bitslicing} and Figure~\ref{fig:SBOX_da}, respectively. Considering an SBOX take some bits derived from a password as input and output 2-bit transform result, the plain implementation
has a range check on the password input and a secret-dependent table lookup while bit-slicing does not.

>>>>

\begin{figure}[h!]
    \centering
    \begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.0\textwidth, frame=none]
uint8_t password = input();
a = *password & 0b001;
b = (*password & 0b010) >> 1;
c = (*password & 0b100) >> 2;
na = ~a & 1;
nb = ~b & 1;
nc = ~c & 1;
t0 = (b & nc);
t1 = (b | nc);
l = (a & nb) | t0;
r = (na & t1) | t0;
ret = l << 1 + r;
\end{lstlisting}
\caption{SBOX with bitslicing}
\label{fig:SBOX_bitslicing}
\end{figure}
We test \tool\ on bit-slicing. We adopt the SBOX
implementations, commonly used in block ciphers such as DES and AES, with and
without bit-slicing, and apply \tool{} to confirm the mitigation. The SBOX implementation with and without bit-slicing are shown in Figure~\ref{fig:SBOX_bitslicing} and Figure~\ref{fig:SBOX_da}, respectively. Considering an SBOX take some bits derived from a password as input and output 2-bit transform result, the plain implementation
has a range check on the password input and a secret-dependent table lookup while bit-slicing does not.
